### 2021-02-02 research project/sections/Analysis_of_results.tex
""

The arithmetic mean of a decimal place was caluclated for 100 trials and the data points 
in the table shown below were found (rounded to 3 s.f.):

>>>>

The arithmetic mean of a decimal place was caluclated for 100 trials and the data points 
in the table shown below were found (rounded to 3 significant figures). The values for the decimal place 
0 have been dropped as it would not be logical to include them.
